Random Generation of Rich \\ Abstract Data Type Values

### 2019-01-29 paper/synthesis.tex
Added logo
Check point

\section{Prediction of Distributions} \label{sec:synthesis}

Characterizing the distribution of values of an arbitrary random generator is a
hard task.
%
It requires to model every random choice that it could possibly make to generate
a value.
%
In a recent work \tocite, we have shown that it is possible to
\emph{analitically} predict the average distribution of data constructors
produced by a random generators automatically derived considering only ADT
definitions---like the one presented on Section \ref{sec:randomtesting}.
%
For this purpose, we found that random generation of ADT values can be
characterized using the theory of \emph{branching processes} \tocite.
%
This probabilistic theory was originally conceived to predict the growth and
extinction of royal family trees the Victorian Era, being later applied to a
wide variety of research areas.
%
In this work we extend this model to predict the average distribution of values
of random generators derived considering structural information coming from
functions pattern matchings and abstract interfaces.

>>>>

\section{Predicting Distributions} \label{sec:synthesis}

Characterizing the distribution of values of an arbitrary random generator is a
hard task.
%
It requires to model every random choice that a generator could possibly make to
generate a value.
%
In a recent work \cite{DBLP:conf/haskell/MistaRH18}, we have shown that it is
possible to \emph{analitically} predict the average distribution of data
constructors produced by a random generators automatically derived considering
only ADT definitions---like the one presented on Section
\ref{sec:randomtesting}.
%
For this purpose, we found that random generation of ADT values can be
characterized using the theory of \emph{branching processes} \cite{gw1875}.
%
\footnote{
%
This probabilistic theory was originally conceived to predict the growth and
extinction of royal family trees the Victorian Era, being later applied to a
wide variety of research areas.}
%
In this work we extend this model to predict the average distribution of values
of random generators derived considering structural information coming from
functions pattern matchings and abstract interfaces.
